A Multiresolution Framework for One Dimensional Neural Field Modelling

### 2011-02-27 Multiresolution_framework/ltx/manuscript.tex
edit to  Bsspline model

and where the kernel approximation coefficient vector $\boldsymbol \alpha_{j_0}$  and the field approximation coefficient vector $\mathbf{x}_{t,j_{0}}$ comprise all the coefficients $\left\lbrace\alpha_{j_0,\mathbf l}:\mathbf{l} \in \mathbb{Z}^d \right\rbrace $ and $\left\lbrace x_{t,j_0,\mathbf l}: \mathbf{l} \in \mathbb{Z}^d\right\rbrace$ respectively. The kernel detail coefficient vectors $\boldsymbol \beta_{j}$ and the field detail coefficient vectors $\check{\mathbf{x}}_{t,j}$ are defined by
 \boldsymbol\beta_{j}^\top=\left[\boldsymbol\beta_{j}^{(1)\top} \quad \boldsymbol\beta_{j}^{(2)\top} \cdots \boldsymbol\beta_{j}^{(2^d-1)\top}\right] 
\check{\mathbf{x}}_{t,j}^\top=\left[\check{\mathbf{x}}_{t,j}^{(1)\top} \quad \check{\mathbf{x}}_{t,j}^{(2)\top} \cdots \check{\mathbf{x}}_{t,j}^{(2^d-1)\top}\right] 
where the vector $\boldsymbol\beta_{j}^{(i)}$ contains all the coefficient $\left\lbrace \beta_{j,\mathbf l}^{(i)} :\mathbf{l} \in \mathbb{Z}^d\right\rbrace$ and the vector $\check{\mathbf{x}}_{t,j}^{(i)}$ contains all the coefficient $\left\lbrace  \check x_{t,j,\mathbf l}^{(i)}:\mathbf{l} \in \mathbb{Z}^d\right\rbrace$. 

@@

By exploiting properties (\ref{eq:BsplineConvolution}) and (\ref{eq:BsplineInnerProduct}) the  integrals (\ref{eq:ConstructionIntegral1}) and (\ref{eq:ConstructionIntegral2}) can be computed. In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, scaling and wavelet basis functions should be expanded  in terms of $N_m$ at the appropriate scale. It is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \cite{Unser1993}: 
 \left\langle \psi_{m;j_1,l_1}(s),\psi_{m;j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
\label{PsiPsiOrthogonality}
 \left\langle \phi_{m;j_1,l_1}(s),\psi_{m;j_2,l_2}(s)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2
\label{PhiPsiOrthogonality}
 Where the subscript $m$ is introduced to $\phi_{j,l}(s)$ and $\psi_{j,l}(s) $ to indicate the $m$th order B-spline scaling and wavelet functions.  
% In the two dimensional case, the convolution integral can be factorised as follows, e.g. 
% \setlength{\arraycolsep}{0.14em}
% \begin{IEEEeqnarray}{!l l }
%  \phi_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right)\ast \psi^{1}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)&=\left[\phi_{m;j,l_1}\left(s_{1}\right)\ast\phi_{m;j,l'_1}\left(s_{1}\right)\right] \nonumber \\
% &\times \left[ \phi_{m;j,l_2}\left(s_{2}\right) \ast \psi_{m;j,l'_2}\left(s_{2}\right)\right] \nonumber \\
% &
% The preceding factorisation can be also applied to the 2D-inner product integral. Non-zero quantities can  be then expressed by
% \setlength{\arraycolsep}{0.14em}
% \begin{IEEEeqnarray}{!l l }
% \left\langle \phi_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\phi_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle &=\left\langle \phi_{m;j,l_1}\left(s_{1}\right),\phi_{m;j,l'_1}\left(s_{1}\right)\right\rangle \nonumber \\
% & \times\left\langle \phi_{m;j,l_2}\left(s_{2}\right) , \phi_{m;j,l'_2}\left(s_{2}\right)\right\rangle \nonumber \\
% &
% likewise we can compute 
% $\left\langle  \psi^{1}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\psi^{1}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle$
% , \\
% $\left\langle  \psi^{2}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right),\psi^{2}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle$ and \\
% $
% \left\langle \psi^{3}_{m;j,\mathbf{l}}\left(s_{1},s_{2}\right), \psi^{3}_{m;j,\mathbf{l'}}\left(s_{1},s_{2}\right)\right\rangle $. \\ \\
In this work, 4th order cardinal B-spline scaling and wavelet functions are used therefore, to compute the integrals (\ref{eq:ConstructionIntegral1}) and (\ref{eq:ConstructionIntegral2})  the $8$th and $12$th order B-spline values at integer points are  required and can be found in \cite{Goswami1999}.

@@

\begin{equation}\label{eq:upsilon0}
 \boldsymbol\upsilon_0=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i} \quad,
\begin{equation}\label{eq:upsilon1}
 \boldsymbol\upsilon_1=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i} \quad,
\begin{equation}\label{eq:Upsilon}
 \boldsymbol\Upsilon=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i},

>>>>

and where the kernel approximation coefficient vector $\boldsymbol \alpha_{j_0}$  and the field approximation coefficient vector $\mathbf{x}_{t,j_{0}}$ comprise all the coefficients $\left\lbrace\alpha_{j_0, l}:l \in \mathbb{Z} \right\rbrace $ and $\left\lbrace x_{t,j_0, l}: l \in \mathbb{Z}\right\rbrace$ respectively. 
Similarly the kernel detail coefficient vectors $\boldsymbol\beta_{j}$ contains all the coefficient $\left\lbrace \beta_{j,l} :l \in \mathbb{Z}\right\rbrace$ and the vector $\check{\mathbf{x}}_{t,j}$ contains all the coefficient $\left\lbrace  \check x_{t,j, l}:l \in \mathbb{Z}\right\rbrace$. 

@@

By exploiting properties (\ref{eq:BsplineConvolution}) and (\ref{eq:BsplineInnerProduct}) the  integrals (\ref{eq:Lambdax}) and (\ref{eq:Lambdatheta}) can be computed. In order to calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, scaling and wavelet basis functions should be expanded  in terms of $N_m$ at the appropriate scale. 
In this work, 4th order cardinal B-spline scaling and wavelet functions are used therefore, to compute the integrals (\ref{eq:Lambdax}) and (\ref{eq:Lambdatheta})  the $8$th and $12$th order B-spline values at integer points are  required and can be found in \cite{Goswami1999}.

@@

\begin{align}\label{eq:upsilon0}
 \boldsymbol\upsilon_0&=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\\ 
 \boldsymbol\upsilon_1&=\xi\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}\label{eq:upsilon1} \\
 \boldsymbol\Upsilon&=T_s\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}\label{eq:Upsilon}
